---
title: "EDA + Visualziation + Text Mining for Wine Products"
author: "Tianze Hua"
date: "3/5/2022"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

```{r}
library(pacman)
p_load(tidyverse, kableExtra, magrittr, 
       knitr, ggrepel, ggwordcloud, readr, tm, 
       SnowballC, wordcloud,RColorBrewer, wordcloud2, sjPlot)
search()
```

```{r}
md <-read.csv("Wine_tasting.csv",sep=",", na.strings ="" )
```

```{r}
glimpse(md)
```

### Count the levels of character columns, range of interger columns, count number of NAs
``` {r}
# count levels of all the character columns
md %>%
  select(-"X") %>% 
  select_if(is.character) %>%
  mutate_all(as.factor) %>% 
  map(levels) %>% 
  map(length)


md %>% 
  select(-X) %>% 
  select_if(is.character) %>%
  summarize_all(funs(sum(is.na(.)))) -> lvl2

# count the range of each integer columns
md %>% 
  select_if(is.integer) %>% 
  na.omit() %>% 
  lapply(range)

# count the NA and blank fields in each column
md %>% 
  select(-X) %>% 
  summarize_all(funs(sum(is.na(.)))) %>% 
  t() %>% 
  as.data.frame() %>% 
  filter(V1>0) %>% 
  rename(Num_of_NA = V1) ->s2

# showing missing proportion of each column of our dataset
lvl2 %>% 
  t() %>% 
  as.data.frame() %>% 
  filter(V1 >0) %>% 
  mutate(NA_prop = paste0(100*round(V1/1000, 5), "%", sep='')) %>% 
  rename(Number_of_NA = "V1") %>% 
  kbl(caption = "NA proportion of Each Character Columns") %>%
  kable_classic_2(full_width = F,
                  html_font = "Cambria")


```

### Data Cleanning
```{r data cleanning}
# We only going to remove the observation without country, price field.

md %<>% 
  drop_na(country, price)

md %<>%
  select(-X)

# remove all the foreign characters of the entire dataset for better understanding
md %<>% 
  mutate_all(funs(gsub("[[:punct:]]", "", .)))
  

dim(md)


# Don't forget to change chr price to numeric one
md$price <- as.numeric(md$price)
md$points <- as.numeric(md$points)
```

### Country Factor
```{r average price by country}
# market share by countries
md %>% 
  select(country,region_1) %>% 
  group_by(country) %>% 
  summarize(n=n()) %>%
  filter(n>30)  %>% 
  mutate(country = fct_reorder(country, desc(n))) %>% 
  ggplot(aes('',n, fill=country))+
  geom_bar(stat="identity",width=1, color = "white")+
  theme(axis.ticks.y = element_blank(),
      axis.text.y = element_blank(),
      axis.text.x = element_blank())+
  coord_polar(theta="y")+
  scale_fill_brewer(palette = "Set3")+
  theme_void()+
  geom_text(aes(label=paste(round(100*n/sum(n),0),"%",sep="")), 
            position = position_stack(vjust = 0.5),size=3)+
  coord_polar(theta = "y")+
  labs(title = 'Market Share by Country',
       subtitle = "Only showing countries with more than 30 wine products")+
  scale_fill_discrete(name = "Country")+
  theme(plot.title = element_text(size = 13),
        plot.subtitle = element_text(size = 8))
  

# mean price by country
md %>% 
  select(country, price) %>% 
  group_by(country) %>%
  summarize(price = round(mean(price),1)) %>% 
  arrange(desc(as.numeric(price))) -> md_cty 

md_cty %>% 
  mutate(country = fct_reorder(country, price)) %>%  
  ggplot(aes(country, price, fill = country))+
  geom_bar(stat="identity", width=1, color = "white")+
  theme_bw()+
  theme(legend.position = "none")+
  scale_x_discrete(
    labels = function(country) str_wrap(country, width = 7))+
  geom_text(aes(label=paste(price,"$", sep="")), size=3,hjust=1)+
  coord_flip()+
  labs(x="Country",
       y="Average Price",
       title = "Average Wine Price from Each Country ")

md %>% 
  select(country) %>% 
  group_by(country) %>% 
  summarize(n =n()) %>% 
  arrange(desc(n)) -> mdx

mdx <- c(mdx[1:5,1])
md %>% 
  select(country, price) %>% 
  filter(country %in% unlist(mdx),
         price <100) %>% 
  mutate(country = fct_reorder(country, desc(price))) %>% 
  ggplot(aes(country, price, fill=country))+
  geom_boxplot()+
  geom_jitter(size = 0.4, alpha = 0.7, color ="#7468de" )+
  theme_bw()+
  scale_fill_brewer(palette = "Set3")+
  labs(title="Boxplot for Wine Price in Each Country",
       y = "Price",
       X = "Country")+
  theme(legend.position="none")
  
# Confidence interval for all over the world and US wine mean price
md %>% 
  lm(price~1,.) %>% 
  confint(level=0.99) %>% 
  kbl(caption = "99% Confidence Interval for Average Wine Price") %>%
  kable_classic_2(full_width = F,html_font = "Cambria")

md %>% 
  filter(country == "US") %>% 
  lm(price~1,.) %>%
  confint(level = 0.99) %>% 
  kbl(caption = "99% Confidence Interval for Average Wine Price in US") %>%
  kable_classic_2(full_width = F,html_font = "Cambria")

```
we are at a 99% confidence interval to state that the mean price of wine of US would lie between 35.8 and 42.2 dollars, and that for the world is between 33.38 and 41.34.


### Province VS Number of Products
```{r number of }
colnames(md)

# Province with more than 30 wine brands
md %>% 
  select(province) %>% 
  group_by(province) %>% 
  summarise(n = n()) %>% 
  arrange(desc(n)) %>% 
  filter(n >30) %>% 
  mutate(province = fct_reorder(province,desc(n))) %>% 
  ggplot(aes(province, n, fill=province)) +
  geom_bar(stat="identity") +
  theme_bw() +
  labs(x = "Province", 
       y = "number of brands of wine Products", 
       title = "Province with more than 30 wine Products")+
  geom_text(aes(label = n), vjust = 1.3)

# if California is outstreched the scale a little bit too much
md %>% 
  select(province) %>% 
  group_by(province) %>% 
  summarise(n = n()) %>% 
  arrange(desc(n)) %>% 
  filter(n > 19, n < 60) %>% 
  mutate(province = fct_reorder(province,desc(n))) %>% 
  ggplot(aes(province, n, fill=province)) +
  geom_bar(stat="identity") +
  theme_bw() +
  labs(x = "Province", 
       y = "Number of brands of wines produced", 
       title = "Number of wine brands of each province",
       subtitle = "excludes Player California")+
  geom_text(aes(label = n), vjust = -0.15, size = 3)+
  scale_x_discrete(
    labels = function(province) str_wrap(province, width = 2))+
  theme(legend.position = "none")

```

Province vs AVG price
```{r avg price for each province}
md %>% 
  select(province, price) %>% 
  na.omit() %>% 
  group_by(province) %>% 
  summarize(province_avg = sum(price)/n()) %>% 
  arrange(desc(province_avg)) -> mad2

mad2 <- c(mad2[1:8,1])

md %>% 
  select(province, price) %>% 
  na.omit() %>% 
  group_by(province) %>% 
  summarize(province_avg = sum(price)/n()) %>% 
  filter(province %in% unlist(mad2)) %>% 
  arrange(desc(province_avg)) %>% 
  mutate(province = fct_reorder(province, province_avg)) %>% 
  ggplot(aes(province, province_avg, fill = province))+
  geom_bar(stat="identity")+
  theme_bw()+
  labs(x = "",
       y = "Price",
       title = "Price of wine")+
  scale_fill_brewer(palette = "Dark2", direction = -1)+
  scale_x_discrete(labels = function(country) str_wrap(country, width = 7))+
  coord_flip()+
  theme(legend.position = "none")+
  geom_text(aes(label=paste(round(province_avg,2),"$", sep="")),hjust=1.1)+
  labs(title = "Most Expensive Origination Province of Wine")
  

md %>% 
  select(price) %>% 
  filter(price<150) %>%
  ggplot(aes(price))+
  geom_density(fill="#69b3a2", 
               color="#e9f0e9", 
               alpha=0.7)+
  theme_minimal()+
  labs(x = "",
       y = "price",
       title = "Price of wine")+
  scale_x_continuous(breaks=round(seq(0,160, by = 10),1))+
  labs(title = "Density Function of Price Distribution",
       subtitle = "Exclued 16 (0.017%) Products Pricing over 150$",
       x = 'Price',
       y = 'Density')+  
  theme(plot.title = element_text(size = 13),
        plot.subtitle = element_text(size = 8))
  
  
```


### Distribution of Price along with correlation between Price and Points
```{r }
md %>% 
  select(country) %>% 
  group_by(country) %>% 
  summarize(n =n()) %>% 
  arrange(desc(n)) -> mdx8

mdx8 <- c(mdx8[1:8,1])
md %>% 
  select(price, points) %>% 
  filter(price<150) %>% 
  na.omit() %>% 
  ggplot(aes(price))+
  geom_histogram(bins=30, fill = "#6298d1", colour="white", lwd = 0.3)+
  labs(title="Distribution of Wine Price",
       x = "Price",
       y = "Count")+
  stat_bin(geom='text', color='black', 
           aes(label=..count..),
           size =3,vjust=-0.3)+
  theme_bw()+
  scale_x_continuous(breaks= seq(0,150,10),limit=c(0,150,15))

md %>% 
  select(price, points, country) %>% 
  na.omit() %>% 
  filter(country %in% unlist(mdx8)) %>% 
  mutate(country = fct_reorder(country,desc(country))) %>% 
  ggplot(aes(price, points))+
  geom_jitter(aes(colour=country), alpha=0.7, size = 0.8)+
  theme(legend.position = "bottom",
        legend.title = element_text(size = 8),
        legend.text = element_text(size = 8))+
  geom_smooth()+
  labs(title="Linear Regression for Wine Price and Points",
       y = "Points",
       x = "Price")+
  scale_x_continuous(breaks= seq(0,400,20),limit=c(0,400,20))


lm1 <- lm(points~price, data=md)
summary(lm1)

md %>% 
  select(price, points, winery, title) %>% 
  filter(price<150) %>% 
  na.omit() %>% 
  mutate(ratio = points/price) %>% 
  ggplot(aes(price, points, colour=ratio))+
  geom_jitter(alpha=0.7, size = 0.8)+
  theme(legend.position = "none")+
  geom_label_repel(aes(label = ifelse(ratio>1.05 & price > 80, winery, NA)), 
                   box.padding = 0.5,max.overlaps = 90)+
  labs(title="Guide for Picking the High PP Ratio Wine Under 150$",
       y = "points",
       x = "Price") +
  theme(plot.title = element_text(size = 13),
      plot.subtitle = element_text(size = 8))+
  scale_x_continuous(breaks=round(seq(0,160, by = 20),1))+
  scale_y_continuous(limit=c(80,100,5))


```

### Data selection for Word Mining
```{r}
md %>% 
  filter(points/price> 0.8) -> md_good
corpus = Corpus(VectorSource(md_good$description))
corpus
md_good$description %>% 
  VectorSource() %>% 
  Corpus -> corpus
```

### Word Processing
```{r}
corpus %>% 
  tm_map(PlainTextDocument) %>% 
  tm_map(tolower) %>% 
  tm_map(removePunctuation) %>% 
  tm_map(stemDocument, language = "english") %>%
  tm_map(stripWhitespace) -> corpus

corpus <- tm_map(corpus,removeWords, stopwords("english"))
```

```{r}
corpus %>% 
  TermDocumentMatrix() %>% 
  as.matrix() %>% 
  rowSums() %>% 
  sort(decreasing = TRUE) -> mat1

word_f <- data.frame(word = names(mat1), freq=mat1)
```

Keyword for Picking the Right Wine
```{r wordcloud }
word_f %>% 
  filter(word != "wine") %>% 
  wordcloud2()

# it does not show in a pdf output
```

